\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{etex}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{370,000.00}


\begin{document}
\title{Polycommit: Forming Habits Through Gamification}
% \titlenote{Produces the permission block, and
%  copyright information}


\begin{abstract}
\par Educational software is infamous for being difficult to use and not engaging. With \textit{Polycommit,} we demonstrate that through gamification and by learning from user behavior, we can create educational software that improves retention of course content and improves test scores.

\par Using learning techniques such as spaced repetition and variable rewards scheduling, we created a learning platform that is engaging and compelling for users to use. We took favorite features from existing learning platforms such as Duolingo and Memrise, and refined the app's design based on feedback and data from users. Overall, we show that with polish and care shown to the user's motivations, we can create an engaging educational app that students will actually want to use, and enjoy using.

\par We developed \textit{Polycommit} for use with several Cal Poly classes. We worked directly with teachers to create questions that drilled down into specific class concepts. We tested the app in 4 different classes, with 130 students signed up. We found that students who used the application performed better on the midterm. We also found that students overall had a positive experience while using the application.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
% TO DO maybe?

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{Education, Gamification}

\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc} 

\end{document}
